---
title: "HW 4"
output: html_document
date: "2024-07-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
############################################################################################
# Clear workspace 
rm(list = ls())
############################################################################################

#######################################################################################################
#######################################################################################################
##################################LOADING PACKAGES#####################################################

################################################################################
#Do tryCatch here

tryCatch(require(pacman),finally=utils:::install.packages(pkgs='pacman',repos='http://cran.r-project.org'));
require(pacman)

##if the above doesn't work, use this code##
##tryCatch
#detach("package:pacman", unload = TRUE)
#install.packages("pacman", dependencies = TRUE)
# ## install.packages("pacman")
pacman::p_load(openxlsx, 
               tidyverse, 
               devtools,
               conflicted,
               lubridate,
               sentimentr)

#Loading libraries
library(openxlsx)
library(tidyverse)
library(devtools)
library(conflicted)
library(lubridate)
library(sentimentr)
```
Setting my conflict prefer
```{r}
#conflict prefer
conflict_prefer("filter", "dplyr")
```

Loading the Honeywell data
```{r}
library(readr)
Data <- read_csv("C:/Users/smjoh/Downloads/glassdoortest1.csv")
```

Let's get our column names.

```{r}
cat(colnames(Data), sep = ",\n")
```

column names
```{r}
colnames(Data)
```

Change X1 to ID

```{r}
Data <- Data %>%
    rename(ID = "...1")
```

We will just look at the Pros for now.

Notice we are creating a new df called Comments_df so that we don't touch the original Data df. This is helpful because we will be slicing, dicing, scattering, etc. to the df in order to split out the text in various ways.



```{r}
#' <!--####################################################################################################### -->
#' <!--####################################################################################################### -->
#' <!--####################################################################################################### -->
#' <!--####################################################################################################### -->
#' <!--####################################################################################################### -->
#' <!--#####################BRUTE FORCE TOPIC CLASSIFICATION USING REGEX###################################### -->

Comments_df <- Data %>%
    select(c(ID, pros)) %>%
    filter(!is.na(pros)) %>%
    rename('comments_pros' = 'pros')

Comments_df2 <- Data %>%
    select(c(ID, cons)) %>%
    filter(!is.na(cons)) %>%
    rename('comments_cons' = 'cons')

```


```{r}
Comments_df <- Comments_df %>%
  as_tibble() %>%
  mutate(comments_pros = str_replace_all(comments_pros, "\uFFFD", "")) 

Comments_df2 <- Comments_df2 %>%
  as_tibble() %>%
  mutate(comments_cons = str_replace_all(comments_cons, "\uFFFD", ""))
```

Convert everything to lowercase for simplicity.

```{r}
#Converting to lower case

Comments_df <- Comments_df %>%
    mutate(comments_pros = tolower(comments_pros))

Comments_df2 <- Comments_df2 %>%
    mutate(comments_cons = tolower(comments_cons))

```

Remove all line breaks.

```{r}
#Remove all line breaks
Comments_df$comments_pros <- gsub("[\r\n]", "", Comments_df$comments_pros)

Comments_df <- Comments_df %>%
    select(ID, comments_pros) %>%
    na.omit()

Comments_df2$comments_cons <- gsub("[\r\n]", "", Comments_df2$comments_cons)

Comments_df2 <- Comments_df2 %>%
    select(ID, comments_cons) %>%
    na.omit()
```

Now let's create our first known topic. We'll go with benefits for now.

Common ones you may want to look at are:

* Benefits
* Career advancement
* Compensation
* Direct Manager
* General Management 
* Safety

What others can you think of?

You can also do subcategories such as:

* Benefits-Health
* Benefits-Paid Time Off

What others can you think of?
#OUR HW
Could you build out your own classifer with ~20 or so meta categories and subcategories as needed?

```{r}
#Creating a beginning using `now` from lubridate.
#After we run everything, we will create `end_time <- now()` along with `print(difftime(end_time, start_time))` as the last line of code after everything we are concerned about has run.

start_time <- now()
```


```{r}
#' <!--#################################### BENEFITS ######################################################### -->

# Define patterns for benefits comments
benefits <- c('\\brx\\b', 
              '^.*medic.*$', 
              '(?=.*bene)(?=.*(?:health))', 
              '(?=.*coverage)(?=.*(?:medic|deduct|prescrip|insur|drug|health|dependent))', 
              '\\b(?:health\\W+(?:\\w+\\W+){0,1}?care)\\b', 
              '\\bhealthcare\\b', 
              '\\bhealth\\s?care\\b', 
              '\\b(?:medical\\W+(?:\\w+\\W+){0,3}?benefits|benefits\\W+(?:\\w+\\W+){0,3}?medical)\\b', 
              '^.*vacation.*$',
              '\\bpto\\b'
)

benefits_pattern <- paste(benefits, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- Comments_df %>%
  mutate(benefits = ifelse(grepl(benefits_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- Comments_df2 %>%
  mutate(benefits = ifelse(grepl(benefits_pattern, comments_cons, perl = TRUE), "Y", "N"))

```


```{r}
#' <!--####################################################################################################### -->

# Define patterns for benefits and insurance comments
benefits_insurance <- c('(?=.*insur)(?=.*(?:medic|dental|life|vision|supplement|disabl))',
                        '\\b(?:insurance\\W+(?:\\w+\\W+){0,1}?premium)\\b',
                        '\\binsurance\\b')

benefits_insurance_pattern <- paste(benefits_insurance, collapse = "|")

# Apply the pattern to both pros and cons comments, creating new columns in TEST and TEST2 directly
TEST <- TEST %>%
  mutate(benefits_insurance = ifelse(grepl(benefits_insurance_pattern, comments_pros, perl = TRUE), "Y", "N"))

TEST2 <- TEST2 %>%
  mutate(benefits_insurance = ifelse(grepl(benefits_insurance_pattern, comments_cons, perl = TRUE), "Y", "N"))

```

Ok, now let's do compensation.

```{r}
#' <!--####################################################################################################### -->
#' <!--####################################################################################################### -->
#' <!--################################# COMPENSATION ######################################################## -->
# Define patterns for compensation comments
compensation <- c('\\bsalary\\b', 
                  '^.*compen.*$',
                  '\\bpay\\b',
                  '^.*incent.*$',
                  '^.*rate.*$',
                  '^.*money.*$')

compensation_pattern <- paste(compensation, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(compensation = ifelse(grepl(compensation_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(compensation = ifelse(grepl(compensation_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Work environment category
```{r}
# Define patterns for work environment comments
work_environment <- c(
  '\\bcoworker\\b',
  '\\bcolleague\\b',
  '\\bteam\\b',
  '\\bmanagement\\b',
  '\\bmanager\\b',
  '\\boffice\\s?space\\b',
  '\\boffice\\b'
)

work_environment_pattern <- paste(work_environment, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(work_environment = ifelse(grepl(work_environment_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(work_environment = ifelse(grepl(work_environment_pattern, comments_cons, perl = TRUE), "Y", "N"))


```
Work-life balance category
```{r}
# Define patterns for work life balance comments
work_life_balance <- c(
  '\\bwork\\s?life\\s?balance\\b',
  '\\bflexible\\s?hours\\b',
  '\\bwork\\s?from\\s?home\\b',
  '\\bovertime\\b',
  '\\bstress\\b',
  '\\bholiday\\b'
)


work_life_balance_pattern <- paste(work_life_balance, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(work_life_balance = ifelse(grepl(work_life_balance_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(work_life_balance = ifelse(grepl(work_life_balance_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Job security category
```{r}
# Define patterns for job security comments
job_security <- c(
  '\\bjob\\s?security\\b',
  '\\bstability\\b',
  '\\blayoffs?\\b',
  '\\bcontract\\b'
)


job_security_pattern <- paste(job_security, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(job_security = ifelse(grepl(job_security_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(job_security = ifelse(grepl(job_security_pattern, comments_cons, perl = TRUE), "Y", "N"))
```
Career Development category
```{r}
# Define patterns for career development comments
career_development <- c(
  '\\btraining\\b',
  '\\bmentorship\\b',
  '\\bpromotion\\b',
  '\\bpromote\\b',
  '\\bcareer\\s?growth\\b',
  '\\blearning\\b',
  '\\bdevelop\\b'
)



career_development_pattern <- paste(career_development, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(career_development = ifelse(grepl(career_development_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(career_development = ifelse(grepl(career_development_pattern, comments_cons, perl = TRUE), "Y", "N"))
```
Company culture category
```{r}
# Define patterns for company culture comments
company_culture <- c(
  '\\bdiversity\\b',
  '\\binclusion\\b',
  '\\bcompany\\s?values\\b',
  '\\bengagement\\b',
  '\\brecognition\\b'
)


company_culture_pattern <- paste(company_culture, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(company_culture = ifelse(grepl(company_culture_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(company_culture = ifelse(grepl(company_culture_pattern, comments_cons, perl = TRUE), "Y", "N"))

# Count the number of "yes" values in the category_col
yes_count <- sum(TEST2$company_culture == "Y")

# Print the result
print(yes_count)
```
Job sat category
```{r}
# Define patterns for job satisfaction comments
job_satisfaction <- c(
  '\\bchalleng(?:ing|e)\\b',
  '\\bfulfillment\\b',
  '\\bsatisf(?:ied|ying|action)\\b',
  '\\btask\\s?variety\\b'
)

job_satisfaction_pattern <- paste(job_satisfaction, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(job_satisfaction = ifelse(grepl(job_satisfaction_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(job_satisfaction = ifelse(grepl(job_satisfaction_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Management category
```{r}
# Define patterns for management comments
management <- c(
  '\\bleadership\\b',
  '\\bcommunication\\b',
  '\\bdecision\\s?making\\b',
  '\\bsupport\\b'
)

management_pattern <- paste(management, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(management = ifelse(grepl(management_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(management = ifelse(grepl(management_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Technical resources category
```{r}
# Define patterns for technological resources comments
technological_resources <- c(
  '\\bequipment\\b',
  '\\bsoftware\\b',
  '\\btechnology\\b',
  '\\btech\\b',
  '\\binnovation\\b'
)

technological_resources_pattern <- paste(technological_resources, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(technological_resources = ifelse(grepl(technological_resources_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(technological_resources = ifelse(grepl(technological_resources_pattern, comments_cons, perl = TRUE), "Y", "N"))

```

Employee perks category
```{r}
# Define patterns for employee perks comments
employee_perks <- c(
  '\\bcafeteria\\b',
  '\\bfood\\b',
  '\\bgym\\b',
  '\\bevents?\\b',
  '\\bperks?\\b'
)

employee_perks_pattern <- paste(employee_perks, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(employee_perks = ifelse(grepl(employee_perks_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(employee_perks = ifelse(grepl(employee_perks_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Job autonomy category
```{r}
# Define patterns for job autonomy comments
job_autonomy <- c(
  '\\bdecision\\s?making\\b',
  '\\bindependence\\b',
  '\\bcreative\\b',
  '\\bautonomy\\b'
)

job_autonomy_pattern <- paste(job_autonomy, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(job_autonomy = ifelse(grepl(job_autonomy_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(job_autonomy = ifelse(grepl(job_autonomy_pattern, comments_cons, perl = TRUE), "Y", "N"))

```


```{r}
# Define patterns for job autonomy comments
policies_procedures <- c(
  '\\bbureaucracy\\b',
  '\\befficiency\\b',   
  '\\btransparency\\b',   
  '\\bpolic(?:y|ies)\\b', 
  '\\bprocedures?\\b',    
  '\\bcompliance\\b'      
)

policies_procedures_pattern <- paste(policies_procedures, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(policies_procedures = ifelse(grepl(policies_procedures_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(policies_procedures = ifelse(grepl(policies_procedures_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Location category
```{r}
# Define patterns for location comments
location <- c(
  '\\bcommute\\b',
  '\\bon\\s?site\\b',
  '\\bgeographic\\s?flexibility\\b',
  '\\bconvenient\\b'
)

location_pattern <- paste(location, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(location = ifelse(grepl(location_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(location = ifelse(grepl(location_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Performance evaluation category
```{r}
# Define patterns for performance eval comments
performance_evaluation <- c(
  '\\bfeedback\\b',
  '\\bevaluation\\b',
  '\\breview\\b',
  '\\bperformance\\b',
  '\\bincentives?\\b'
)

performance_evaluation_pattern <- paste(performance_evaluation, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(performance_evaluation = ifelse(grepl(performance_evaluation_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(performance_evaluation = ifelse(grepl(performance_evaluation_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Workload category
```{r}
# Define patterns for workload comments
workload <- c(
  '\\bworkload\\b',
  '\\btask\\b',
  '\\bpressure\\b',
  '\\btime\\s?management\\b'
)

workload_pattern <- paste(workload, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(workload = ifelse(grepl(workload_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(workload = ifelse(grepl(workload_pattern, comments_cons, perl = TRUE), "Y", "N"))

```

International opportunities category
```{r}
# Define patterns for international opportunities comments
international_opportunities <- c(
  '\\bglobal\\s?exposure\\b',
  '\\brelocation\\b',
  '\\binternational\\b',
  '\\bprojects?\\b'
)

international_opportunities_pattern <- paste(international_opportunities, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(international_opportunities = ifelse(grepl(international_opportunities_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(international_opportunities = ifelse(grepl(international_opportunities_pattern, comments_cons, perl = TRUE), "Y", "N"))
```
Company reputation category
```{r}
# Define patterns for company reputation comments
company_reputation <- c(
  '\\breputation\\b',
  '\\bmarket\\s?position\\b',
  '\\bindustry\\s?leader(?:ship)?\\b',
  '\\binnovation\\b'
)

company_reputation_pattern <- paste(company_reputation, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(company_reputation = ifelse(grepl(company_reputation_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(company_reputation = ifelse(grepl(company_reputation_pattern, comments_cons, perl = TRUE), "Y", "N"))

```
Project management category
```{r}
# Define patterns for project management comments
project_management <- c(
  '\\bproject\\b',
  '\\bvariety\\b',
  '\\bcomplex\\b',
  '\\bsupport\\b'
)

project_management_pattern <- paste(project_management, collapse = "|")

# Apply the pattern to pros comments, creating a new column in TEST directly
TEST <- TEST %>%
  mutate(project_management = ifelse(grepl(project_management_pattern, comments_pros, perl = TRUE), "Y", "N"))

# Apply the pattern to cons comments, creating a new column in TEST2 directly
TEST2 <- TEST2 %>%
  mutate(project_management = ifelse(grepl(project_management_pattern, comments_cons, perl = TRUE), "Y", "N"))
```

